---
output:
  pdf_document: default
  html_document: default
---
title: "Quantium Virtual Internship - Retail Strategy and Analytics - Task 1"
mainfont: Roboto
monofont: Consolas
output:
  pdf_document:
  df_print: default
highlight: tango
keep_tex: yes
latex_engine: xelatex
header-includes:
  \usepackage{fvextra}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---
  ```{r setup, include=FALSE}
# set options for R markdown knitting
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(linewidth=80)
```{r knitr line wrap setup, include=FALSE}
# set up line wrapping in MD knit output
library(knitr)
hook_output = knit_hooks$get("output")
knit_hooks$set(output = function(x, options)
{
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth))
  {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n))
      x = strwrap(x, width = n)
    x = paste(x, collapse = "\n")
  }
  hook_output(x, options)
})